---
title: "Biomass Energy Test 2"
author: "Deepak Jaiswal"
date: '2022-11-07'
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
The total dry biomass of a plant (W in tons ha$^{-1}$) at a time $t$ (days) ($t_{peak} \ge$ $t \ge t$~0~) can be approximated by the Gompertz growth function with parameters μ~0~ (specific growth rate at t~0~), D (parameter describing the decay in the specific growth rate), and W~0~ (W at t~0~; a proxy for planting rate or leftover from the previous harvest). The gompertz growth function is given below:
\begin{align}
W = W_{0}e^{\frac{\mu_{0}(1-e^{-Dt})}{D}}
\end{align}
$t$~0~ is the day of emergence and $t_{peak}$ is the day of peak biomass.


The three parameters (W~0~,μ~0~,D) for two bioenergy crops: sugarcane and miscanthus using observations from two experimental sites in Sao Paulo Brazil (tropical climate) and Illinois USA (temperate), respectively, along with the day of emergence and the day of peak biomass, are shown in the table below.





```{r optimized_parameters_for_gompertz_equation, eval=FALSE, include=FALSE}
gompertz_W <- function(W0,mu0,D,t){
  output <- W0*exp(mu0*(1-exp(t*D*(-1)))/D)
  return(output)
}


sugarcane_w = list(t=c(0,100,200,300,360),w=c(1,5,40,80,90))

sugarcane_initial = c(1,0.3,0.065)
objective_function <- function(gompertz_params,observation){
  predicted <- gompertz_W(gompertz_params[1],gompertz_params[2],gompertz_params[3],observation$t)
  error = predicted - observation$w
  E = sum(error^2)
  return(E)
}

sugarcane_parameters <- optim(par = sugarcane_initial,fn = objective_function,observation=sugarcane_w)
sugarcane_parameters
# 0.345142126 0.048789476 0.008296256


miscanthus_w = list(t=c(0,50,100,210),w=c(15,25,50,70))
miscanthus_initial = c(1,0.3,0.065)
miscanthus_parameters <- optim(par = miscanthus_initial,fn = objective_function,observation=miscanthus_w)
miscanthus_parameters
# 12.48171670  0.02291015  0.01219524


## Plotting biomass of sugarcane and miscanthus

t_sugarcane = seq(0,360)
sugarcane_w = gompertz_W(W0=0.345142126 ,mu0 = 0.048789476,D=0.008296256,t=t_sugarcane)
lattice::xyplot(sugarcane_w~t_sugarcane)

t_mxg = seq(0,210)
miscanthus_w <- gompertz_W(W0=12.48171670 ,mu0 = 0.02291015,D=0.01219524,t=t_mxg)
lattice::xyplot(miscanthus_w~t_mxg)

```


|Bioenergy crop|W~0~ (tons ha$^{-1}$) |μ~0~ ($day^{-1}$)| D($day^{-1}$)| t~0~ (days)|  $t_{peak}$ (days)|
|:------------|----:|---:|----:|---:|---:|
|Sugarcane    | 0.345  | 0.048|  0.0082|      0 (5th Jan)|         ~360 (30 Dec)|
|Miscanthus   | 12.481|  0.023|  0.0121|      0(5th Apr)|         ~210 (1 Nov)|

The approximate partitioning of total biomass into various components: stem and leaves (above-ground) and roots and rhizome (below-ground) are given in the table below

|Bioenergy crop| Stem | Leaves| Below-ground|
|:------------|----:|---:|----:|
|Sugarcane    | 0.84  | 0.10|  0.06|     
|Miscanthus ($t \le 100$)  | 0.25|  0.05|  0.7|  
|Miscanthus ($t \gt 100$)   | 0.6|  0.05|  0.35| 


The day of harvest ($t_{harvest}$) for sugarcane coincides with the day of peak biomass $t_{peak}$ to maximize the availability of biomass for the production of bio ethanol. However, Harvesting is delayed for miscanthus so that nutrients can be re-mobilized from above-ground to the below-ground components of the plants and need of fertilization is minimized for the next year.This results in a penalty in terms of availability of biomass for producing bio ethanol, but, at the same time, reduces (or nullify) the requirement of fertilizer application for the next year.

Assume that 

1. miscanthus harvesting is planned for the 15th of March of next year resulting in a gap of 135 days between  ($day^{-1}$ = 345 ) and ($t_{peak}$ = 210). 
2. During the period between $t_{peak}$ and $t_{harvest}$, the standing (on the field) above-ground biomass is lost at a rate of 0.07 tons $day^{-1}$

**Question 1. Draw a curve showing biomass of stem, leaves, and below-ground components on the Y axis (tons ha$^{-1}$) and time ($t$) on the x axis from $t_{0}$ to $t_{harvest}$ for miscanthus and sugarcane. [max score = 5]**


**Question 2.Calculate the amount of biomass that can be transported from 1ha of miscanthus and sugarcane fields to a nearby bio refinery for producing bio ethanol ethanol assuming harvesting occurs on t= $t_{harvest}$ for both sugarcane and miscanthus . [max score =2]**

**Question 3. Calculate the amount of biomass assimilated into the soil of field used for growing sugarcane and miscanthus. You can use fraction of below-ground biomass dying since the date of harvest to the starting of new growing cycle as shown in the table below. [max score =2] **



|Bioenergy crop| Fraction of dead below-ground biomass (between harvest and start of next growth cycle)|
|:----|----:|
|Sugarcane    | 0.5|     
|Miscanthus   | 0.65|  
 


